### 2019-07-01 report/chapter03.Rnw
correction of tes

\section{Small Study Effect and Excess of Singificance Tests}
<<echo=FALSE, warning=FALSE>>=
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

@@

@@

p.dist.bin <- meta.bin %>% ungroup() %>% 
  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 250, label = label), color = "black") + 
  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

@@

  plot.xy(xy.coords(x, y), type = "p", ...)
  box(col = "lightgray")
  rect(xleft = -1.96, ybottom = -1.96, xright = 1.96, ytop = 1.96, density = NULL, angle = 45,
       col = NA, border = "white", lty = 1, lwd = 1.4, 
       ...)
  if (!is.null(corr)) 
    return()

@@

@@

harbord.excess.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + theme(legend.position = "bottom") +
  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
#--------------------------------------------------------------------------------------------------------------------#

@@

number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
                               binary = paste(summary.bin$n[-7], "%"),
                               cont = paste(c(summary.else$n[-6], NA), "%"))
colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")

@@

The meta-analyses fullfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests. The $p$-values for all meta-analyses can be displayed in histograms. Because the tests are methodologically different, the results of each testing method is displayed separately. Furthermore, the outcome types (as defined previously by the variable \texttt{outcome.type}) are also kept separated.\\
The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance. Moreover, the excess significance tests have a mode around $p = 0.4$. The large differences between small study effect tests for binary and continuous outcomes will be subject to discussion.\\
``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}, see \ref{sex:excess.significance}. For continuous and survival outcomes, the names refer to:

\begin{itemize}
\item Egger's test, the weigthed linear regression test as described in section \ref{sec:Egger}
\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
\end{itemize}

@@

\begin{figure}
<<echo=FALSE, fig.height = 9>>=
grid.arrange(p.dist.bin,
             p.dist.cont,
             p.dist.surv, ncol = 1)
@
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses. Especially between small study effects and excess significance tests, we expect some disagreement between tests. A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics. This is done in Figure \ref{fig:test.agreement}. \\
Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.

\begin{figure}
<<echo=FALSE, fig.height = 6, warning=FALSE>>=
corrgram(cor.data, 
         upper.panel=panel.pts.new, lower.panel=panel.cor, 
         cex.labels = 1, cex = .3, cex.cor = 2, pch = 1,
         text.panel=panel.txt, cor.method = "spearman")
@
\caption{Pairs-plot for test statistics of small study effect and excess significance. The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot. The colours indicate magnitude and direction of the correlation coefficients. The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
\label{fig:test.agreement}
\end{figure}

The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points. Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients. In general, small study effect tests align, but the extent to which they align differs. Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Harbord's and Rucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

This can be justified since all tests are supposed to measure the evidence for publication bias. For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation. The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value. If no systematic errors and biases exist between the measurement methods, then

\begin{itemize}
\item the mean of the differences (systematic error) should be around zero
\item the points should scatter independent of the mean of the $p$-values
\end{itemize}

The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
-- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions. This finding suggests that correspondence between the tests is poor. The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.

\begin{figure}
<<echo=FALSE, fig.height = 6.5, warning=FALSE>>=
grid.arrange(egger.thompson.plot, 
             harbord.rucker.plot, 
             harbord.excess.plot, ncol = 1)
@
\caption{Mean - difference plots for logit transformed $p$-values. The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis. Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
\label{fig:mean.diff.test}
\end{figure}

@@

When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result. After applying the bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\& for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes. \\
When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test. \Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes. Again, the numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the bonferroni correction. \\
\Sexpr{both.bin}\% have significant Harbord's test result and significant excesss significance test result  (\Sexpr{both.bin.b}\% with bonferroni). Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.

@@

diff.log.hazard.ratio.ranef <- meta.surv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
                           sign(copas) != sign(ranef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
                                sign(regression) != sign(ranef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio")
#--------------------------------------------------------------------------------------------------------------------#

#Quantile and mean table of differences:
adjustment.diff <- meta.f %>% 
  transmute(est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
                           sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
                                sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),

@@

adjustment.smaller.reg.z.f <- round(length(which(adjustment.diff$reg.z.f > 0))/length(which(!is.na(adjustment.diff$reg.z.f)))*100, 1)

>>>>

\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}
<<echo=FALSE, warning=FALSE>>=
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

@@

#Agreement proportions of publication bias tests:

#Binary:
meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
                                              tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
                                              tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
                                              tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
                                              schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
                                              schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
                                              schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
                                              rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
                                              rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
                                              harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
                                                      tes.d.peter = sum(tes.d.peter == "agree")/n(),
                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
                                                      rucker.peter = sum(rucker.peter == "agree")/n(),
                                                      harbord.peter = sum(harbord.peter == "agree")/n())
meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
                                              tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
                                              tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
                                              tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
                                              schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
                                              schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
                                              schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
                                              rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
                                              rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
                                              harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
agreement.sig.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(tes.d.test),
                                                      tes.d.peter = sum(tes.d.peter == "agree")/sum(tes.d.test),
                                                      tes.d.rucker = sum(tes.d.rucker == "agree")/sum(tes.d.test),
                                                      tes.d.harbord = sum(tes.d.harbord == "agree")/sum(tes.d.test),
                                                      schwarzer.peter = sum(schwarzer.peter == "agree")/sum(schwarzer.test),
                                                      schwarzer.rucker = sum(schwarzer.rucker == "agree")/sum(schwarzer.test),
                                                      schwarzer.harbord = sum(schwarzer.harbord == "agree")/sum(schwarzer.test),
                                                      rucker.peter = sum(rucker.peter == "agree")/sum(rucker.test),
                                                      harbord.peter = sum(harbord.peter == "agree")/sum(peter.test))

binary.tests.agreement <- rbind(agreement.bin, agreement.sig.bin)
rownames(binary.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
                                      "Excess significance, Rucker", "Excess significance, Harbord",
                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
                                      "Rucker, Peter", "Harbord, Peter")
#--------------------------------------------------------------------------------------------------------------------#

#Continuous:
meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(tes.d.test),
                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(tes.d.test),
                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(tes.d.test),
                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))

cont.tests.agreement <- rbind(agreement.cont, agreement.sig.cont)
rownames(cont.tests.agreement) <- c("Agreement (overall)", "Agreement (significance)")
colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson",
                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")

#Survival:
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test + egger.test > 1, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test + begg.test > 1, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test + begg.test > 1, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test + egger.test > 1, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test +tes.d.test > 1, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test + begg.test > 1, "agree", "disagree"))
agreement.sig.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
                                                             thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompson.test),
                                                             tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
                                                             thompson.egger = sum(thompson.egger == "agree")/sum(thompson.test),
                                                             thompson.begg = sum(thompson.begg == "agree")/sum(begg.test),
                                                             egger.begg = sum(egger.begg == "agree")/sum(begg.test))

surv.tests.agreement <- rbind(agreement.surv, agreement.sig.surv)
rownames(surv.tests.agreement) <- c("Agreement (overall)","Agreement (significance)")
colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)",
                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)",
                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")

#Merging:
test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))

@@

p.dist.bin <- meta.bin %>% ungroup() %>% 
  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 200, label = label), color = "black") + 
  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

@@

  plot.xy(xy.coords(x, y), type = "p", ...)
  box(col = "lightgray")
  rect(xleft = -1.644854, ybottom = -1.644854, xright = 1.644854, ytop = 1.644854, density = NULL, angle = 45,
       col = NA, border = "white", lty = 1, lwd = 1.4, 
       ...)
  if (!is.null(corr)) 
    return()

@@

egger.excess.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.egger)+ logit(pval.d.tes)))/2, 
         difference = logit(pval.egger) - logit(pval.d.tes)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point() + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + theme(legend.position = "none") +
  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value excess significance)" )))
#--------------------------------------------------------------------------------------------------------------------#

@@

harbord.excess.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + #theme(legend.position = "bottom") +
  scale_color_manual(labels = c("systematic error", "95 % conf. int."), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
#--------------------------------------------------------------------------------------------------------------------#

@@

number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
                               binary = paste(summary.bin$n[-7], "%"),
                               cont = as.character(paste(c(summary.else$n[-6], NA), "%")))
number.sig.tests <- as.matrix(number.sig.tests)
number.sig.tests[6,3][1] <- "-"

colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")

@@

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with small study effects tests and excess significance tests. We will apply the tests on the original effect size measures, i.e. risk ratios, Hedges $g$ or log hazard ratios. Different tests are applied depending on if the outcomes are of type binary or continuous or survival.\\
Thus, we apply multiple tests on the same data. The results can then be displayed separately to compare the different tests. A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}. \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and survival outcomes, the names refer to:

\begin{itemize}
\item Egger's test, the weighted linear regression test as described in section \ref{sec:Egger}
\item Thompson and Sharp's test, the weighted linear regression test adjusted for between-study heterogeneity, section \ref{sec:Thompson}
\item Begg and Mazumdar's test, the rank test described in section \ref{sec:Begg}
\end{itemize}

@@

\begin{figure}
<<echo=FALSE, fig.height = 9>>=
grid.arrange(p.dist.bin,
             p.dist.cont,
             p.dist.surv, ncol = 1)
@
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, bin width is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that the distributions are (with the exception of Schwarzer's test) skewed to the right for all outcome types, indicating evidence for small study effects and excess significance, respectively. Moreover, the excess significance tests have a mode around $p = 0.4$. There is some discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Survival outcome type results are quite different with very few evidence for small study effects and excess significance. Note that the sample size of survival outcomes is small ($n$ = \Sexpr{dim(meta.surv)[1]}).\\
It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses. A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results.

\begin{figure}
<<echo=FALSE, fig.height = 6, warning=FALSE>>=
corrgram(cor.data, 
         upper.panel=panel.pts.new, lower.panel=panel.cor, 
         cex.labels = 1, cex = .25, cex.cor = 2, pch = 1,
         text.panel=panel.txt, cor.method = "spearman")
@
\caption{Pairs-plot for test statistics of small study effect and excess significance. The lower panel gives the Spearman correlations for the different test statistics, and the upper panel displays a scatterplot. The colors indicate magnitude and direction of the correlation coefficients. The rectangle with white borders displays the area within which both tests have absolute value < 1.64 (dots outside are statistically significant using the 0.1 threshold).}
\label{fig:test.agreement}
\end{figure}

The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points. Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients. In general, small study effect tests align on the diagonal, but the extent to which they align differs. Continuous and survival outcome type tests align more closely than binary outcome tests. While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Egger's and excess significance tests
\item For Harbord's and R\"ucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

This can be justified since all tests are supposed to measure the evidence for publication bias. For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation $f(x)  = \log\frac{p}{1-p}$). The mean $p$-value (($f$($p$-value no. 1) + $f$($p$-value no. 2))/2) is then displayed against the difference between the $f$($p$-value). If no systematic errors and biases exist between the measurement methods, then

\begin{itemize}
\item the mean of the differences should be around zero (systematic error) 
\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
\end{itemize}

Although this is not formally tested, the last criterium seems not to be given when comparing small study effect and excess significance tests. With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions. -- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- However, the systematic error between the compared tests is close to zero, and small study effect tests do probably not show bias when compared to each other. \\
The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests. This suggests that correspondence between the tests is not very good in general.

\begin{figure}
<<echo=FALSE, fig.height = 8.5, warning=FALSE>>=
grid.arrange(egger.thompson.plot, 
             egger.excess.plot,
             harbord.rucker.plot, 
             harbord.excess.plot, ncol = 1)
@
\caption{Mean - difference plots for logit transformed $p$-values. The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis. Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
\label{fig:mean.diff.test}
\end{figure}

@@

Here, it is difficult to say if continuous and survival or binary outcome types show better agreement, since more tests are applied in the binary case, and the continuous and survival outcome type tests have in general more positive findings. Very few meta-analyses are significant, irrespective of the test used, but around 67\% of the dataset is not significant, no matter which test is used. \\
When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result. This also suggests that the overlap between small study effect tests and excess significance is small. After applying the Bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\% for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes. \\
To compare significant findings for small study effect tests and excess significance tests, we limit ourselves to comparison with Harbord's or Egger's test. \Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes. The numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the Bonferroni correction. \\
\Sexpr{both.bin}\% have significant Harbord's test result and significant excess significance test result  (\Sexpr{both.bin.b}\% with Bonferroni). Of the continuous outcomes, we have \Sexpr{both.else}\% with Egger's test and \Sexpr{both.else.b}\% with Bonferroni correction.

@@

diff.log.hazard.ratio.ranef <- meta.surv %>% 
  mutate(fixef = est.fixef, ranef = est.ranef,
         copas = est.copas, regression = est.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(ranef) ~  abs(copas),
                           sign(copas) != sign(ranef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(ranef) ~  abs(regression),
                                sign(regression) != sign(ranef) ~ -abs(regression)),
         fixef = abs(fixef),
         ranef = abs(ranef)) %>% 
  gather(key = "method", value = "adjusted.log.hazard.ratio", copas:regression)  %>% 
  ggplot(aes(x = (ranef - adjusted.log.hazard.ratio))) + 
  geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + xlab("Random effects - adjusted log hazard ratio")
#--------------------------------------------------------------------------------------------------------------------#
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

#Quantile, mean, largerthan and missing table of differences:
adjustment.diff.keep <- meta.f %>% 
  mutate(est.copas.f = case_when(sign(est.copas) == sign(est.fixef) ~  abs(est.copas),
                                 sign(est.copas) != sign(est.fixef) ~ -abs(est.copas)),
         est.reg.f = case_when(sign(est.reg) == sign(est.fixef) ~  abs(est.reg),
                               sign(est.reg) != sign(est.fixef) ~ -abs(est.reg)),
         est.copas.r = case_when(sign(est.copas) == sign(est.ranef) ~  abs(est.copas),
                                 sign(est.copas) != sign(est.ranef) ~ -abs(est.copas)),
         est.reg.r = case_when(sign(est.reg) == sign(est.ranef) ~  abs(est.reg),
                               sign(est.reg) != sign(est.ranef) ~ -abs(est.reg)),

         est.d.copas.f = case_when(sign(est.d.copas) == sign(est.d.fixef) ~  abs(est.d.copas),
                                   sign(est.d.copas) != sign(est.d.fixef) ~ -abs(est.d.copas)),
         est.d.reg.f = case_when(sign(est.d.reg) == sign(est.d.fixef) ~  abs(est.d.reg),
                                 sign(est.d.reg) != sign(est.d.fixef) ~ -abs(est.d.reg)),
         est.d.copas.r = case_when(sign(est.d.copas) == sign(est.d.ranef) ~  abs(est.d.copas),
                                   sign(est.d.copas) != sign(est.d.ranef) ~ -abs(est.d.copas)),
         est.d.reg.r = case_when(sign(est.d.reg) == sign(est.d.ranef) ~  abs(est.d.reg),
                                 sign(est.d.reg) != sign(est.d.ranef) ~ -abs(est.d.reg)),

@@

#--------------------------------------------------------------------------------------------------------------------#
#Tukey mean difference plots for adjustment methods:
